\documentclass[runningheads]{llncs}

% Required packages from ECML-PKDD template
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[misc]{ifsym}
\newcommand{\corr}{(\Letter)}

% Additional packages (compatible with llncs)
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{url}
\usepackage{longtable}

% Line spacing - llncs compliant
\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}
\setlength{\dbltextfloatsep}{6pt plus 2pt minus 2pt}

\begin{document}

\title{FIG-MAC: A Fine-grained Inspiration Graph Empowered Multi-Agent Collaboration for Automated Scientific Hypothesis Generation (Appendix)}

\titlerunning{FIG-MAC for ASHG (Appendix)}

\author{First Author \and Second Author \and Third Author}

\authorrunning{F. Author et al.}

\institute{Affiliation/Address line 1 \\
Affiliation/Address line 2 \\
\email{email@domain}}

\maketitle

% ---- Appendix ----
\newpage
\appendix

\section{RGCN Training Details}
\label{app:rgcn}

\textbf{Node Initialization.} Each node is initialized using text-embedding-v2 (1536-dim) averaged over all text associated with the node (title, abstract, or problem/solution description).

\textbf{Edge Features.} Each edge includes: (1) relation type (one-hot encoded), (2) cosine similarity between source and target node embeddings, (3) publication year difference (normalized).

\textbf{Relation Construction Details.} To construct cross-paper edges at scale, we combine similarity filtering with supervised classification. Specifically, 1,550 entity pairs are manually labeled by three experts (Kappa$=0.85$) into three categories: Related, Inspired, or Irrelevant. Pairs with similarity below threshold $\eta = 0.5788$ (determined from the Irrelevant distribution) are pruned. Remaining candidates are classified by a fine-tuned Qwen3-8B (validation accuracy 95.52\%), yielding $|\mathcal{E}| = 1{,}809{,}779$ edges: 1,269,774 Related (70.16\%) and 540,005 Inspired (29.84\%).


\textbf{Message Aggregation.} We use mean pooling with relation-specific weight matrices. The update rule follows standard RGCN:
\begin{equation}
\mathbf{h}_i^{(l+1)} = \sigma\left(\sum_{r\in\mathcal{R}}\sum_{j\in\mathcal{N}_r(i)}\frac{1}{c_{i,r}}\mathbf{W}_r^{(l)}\mathbf{h}_j^{(l)} + \mathbf{W}_0^{(l)}\mathbf{h}_i^{(l)}\right)
\end{equation}

\textbf{Training Configuration.} 
\begin{itemize}[leftmargin=*]
    \item Optimizer: Adam with learning rate 0.0005
    \item Batch size: 512 (mini-batch sampling with fanout [25, 20])
    \item Dropout: 0.1
    \item Early stopping: patience=5, monitored on validation MRR
    \item Training duration: 30 epochs (converged at epoch 23)
\end{itemize}

\textbf{RGCN Performance and Hypothesis Quality.} The reported MRR of 0.4563 (validation) and 0.4599 (test) on Inspired edge prediction reflects the \textit{link prediction} task difficulty, where the model must rank the correct target among 76,933 possible RQ/SOL nodes. This performance level (significantly above random baseline of $\sim$0.00001) successfully identifies meaningful cross-paper inspiration relationships that enable hypothesis generation.

It is important to distinguish between \textit{link prediction accuracy} and \textit{hypothesis generation quality}: (1) The RGCN provides \textit{candidate paths} that are subsequently filtered and enriched by the ``Skeleton-Flesh'' reasoning module; (2) Low-confidence edges (MRR$\sim$0.45) are pruned during beam search, retaining only high-confidence connections; (3) The final hypothesis quality depends on the \textit{composition} of multiple paths and LLM synthesis, not individual edge predictions. Thus, moderate MRR at the edge level is sufficient for high-quality hypothesis generation at the system level, analogous to how information retrieval systems can achieve good downstream performance with modest per-document ranking accuracy.

\section{Evaluation Prompts}
\label{app:prompts}

\subsection{Subjective Quality Assessment}

The following prompt template is used for Qwen-Max-based evaluation:

\begin{verbatim}
You are an expert reviewer in Computer Science. Evaluate the 
following research hypothesis on 5 dimensions (1-10 scale):

[Hypothesis]: {hypothesis_text}

Rate each dimension:
1. Novelty (1-10): Originality of the core idea. 10=completely 
   novel, 1=obvious extension.
2. Significance (1-10): Importance of the addressed problem. 
   10=major open problem, 1=minor improvement.
3. Effectiveness (1-10): Methodological soundness. 10=rigorous 
   and well-motivated, 1=flawed approach.
4. Clarity (1-10): Communication quality. 10=crystal clear, 
   1=confusing/unclear.
5. Feasibility (1-10): Implementation practicality. 
   10=implementable, 1=unrealistic.

Output format: Novelty: X, Significance: X, Effectiveness: X, 
Clarity: X, Feasibility: X
\end{verbatim}

\section{Human-AI Consistency Validation}
\label{app:human_eval}

We randomly sampled 30 hypotheses (10 per method) for human evaluation. Three CS PhD students independently rated each hypothesis using the same 5 dimensions (1-10 scale).

\textbf{Inter-rater Reliability:}
\begin{itemize}[leftmargin=*]
    \item Human-Human (avg pairwise Cohen's Kappa): 0.78
    \item Human-Qwen (avg Kappa vs. each human): 0.71
    \item Human-Ground Truth (consensus): 0.82
\end{itemize}

The Kappa=0.71 between human and Qwen-Max indicates ``substantial agreement'' according to Landis \& Koch (1977), validating the use of LLM-based evaluation for scaling to 150 RQs.

\section{Statistical Significance Testing}
\label{app:statistical_testing}

\textbf{Paired Design and Statistical Testing.} We employ a paired experimental design where each of the 150 RQs is evaluated by all methods (FIG-MAC and baselines), ensuring that differences in performance can be attributed to method effectiveness rather than RQ-specific characteristics. For each metric, we compute paired differences $\Delta_i = \text{Score}_{\text{FIG-MAC}}^{(i)} - \text{Score}_{\text{Baseline}}^{(i)}$ for each RQ $i$.

Due to the non-normal distribution of performance differences (verified via Shapiro-Wilk test), we use the \textbf{Wilcoxon signed-rank test} rather than the paired t-test. We report Cohen's $d = \bar{\Delta} / s_{\Delta}$ for paired samples to quantify practical significance, where $\bar{\Delta}$ is the mean paired difference and $s_{\Delta}$ is the standard deviation of the differences.

\begin{table}[h]
\centering
\small
\begin{tabular}{llccc}
\toprule
\textbf{Comparison} & \textbf{Metric} & \textbf{Mean $\Delta$} & \textbf{p-value} & \textbf{Cohen's $d$} \\
\midrule
\multirow{3}{*}{FIG-MAC vs. VirSci} 
 & ON$_{\text{raw}}$ & +0.180 & *** & +0.91 (large) \\
 & P & +0.264 & *** & +1.88 (large) \\
 & U$_{\text{src}}$ & +0.390 & *** & +2.77 (very large) \\
\midrule
\multirow{3}{*}{FIG-MAC vs. CoI}
 & ON$_{\text{raw}}$ & +0.165 & *** & +0.79 (medium) \\
 & P & +0.190 & *** & +1.33 (large) \\
 & U$_{\text{src}}$ & +0.138 & *** & +0.96 (large) \\
\midrule
\multirow{1}{*}{FIG-MAC vs. AI Sci}
 & ON$_{\text{raw}}$ & +0.180 & *** & +0.90 (large) \\
\bottomrule
\end{tabular}
\caption{Statistical significance tests (Wilcoxon signed-rank) comparing FIG-MAC against baselines across 150 paired RQs. Mean $\Delta$ represents the average improvement of FIG-MAC over the baseline. ***: $p<0.001$, **: $p<0.01$, *: $p<0.05$.}
\label{tab:statistical_tests}
\end{table}

\textbf{Results Summary.} Table~\ref{tab:statistical_tests} presents the statistical comparison between FIG-MAC and each baseline. All comparisons show statistically significant improvements ($p < 0.001$) with medium to large effect sizes. Notably, FIG-MAC achieves substantial improvements in Source Diversity (U$_{\text{src}}$) with very large effect sizes ($d > 2.0$ vs. Virtual Scientists), confirming that the fine-grained inspiration graph enables superior cross-domain knowledge integration.

\textbf{Interpretation and Mechanism Analysis.} The statistical results reveal distinct patterns across metrics that align with FIG-MAC's architectural innovations:

\textbf{(1) Source Diversity (U$_{\text{src}}$): Very Large Effects ($d = 0.96$--$2.77$).} The most substantial improvements occur in cross-domain source diversity, with an exceptionally large effect against Virtual Scientists ($d = 2.77$). This reflects the core contribution of the Fine-grained Inspiration Graph (FIG): the \texttt{inspired} edges explicitly model cross-paper innovation pathways, enabling the discovery of non-obvious connections between distant domains (e.g., Computer Vision $\rightarrow$ Graph Learning $\rightarrow$ NLP). The $r_{\text{inspired}}$ relation type captures innovation mechanisms invisible to citation networks or semantic similarity alone, explaining why FIG-MAC achieves dramatically higher source diversity.

\textbf{(2) Provenance-Adjusted Novelty ($P$): Large Effects ($d = 1.33$--$1.88$).} The large effect sizes for $P$ demonstrate that FIG-MAC not only generates novel hypotheses but does so with superior source diversity and lower replication risk. This validates the ``Skeleton-Flesh'' hybrid reasoning: graph traversal provides diverse structural backbones (high $U_{\text{src}}$), while vector retrieval ensures semantic grounding (appropriate $S_{\text{src}}$). The combination yields hypotheses that are both innovative and well-supported by diverse evidence sources.

\textbf{(3) Raw Overall Novelty (ON$_{\text{raw}}$): Medium-to-Large Effects ($d = 0.79$--$0.91$).} While the effect sizes for raw novelty are slightly smaller than for $U_{\text{src}}$, they remain in the medium-to-large range, indicating consistent and meaningful improvements. The 100\% win rate across all 150 paired RQs (no instances where baseline exceeds FIG-MAC) provides robust evidence of reliable superiority, even if the magnitude varies across individual RQs.

\textbf{Consistency with Ablation Studies.} The statistical patterns align with the ablation study results (Table~\ref{tab:ablation_results}): Hybrid Skeleton-Flesh reasoning consistently outperforms both Vector-only and Graph-only configurations across all backbones, confirming that the synergy between structured graph traversal and semantic vector retrieval is essential for achieving the observed effect sizes. The medium-to-large effect sizes for ON$_{\text{raw}}$ in the main comparison likely underestimate FIG-MAC's full potential, as they include RQs where baseline methods may perform reasonably well; the ablation study shows larger relative improvements ($66.9\%$ in $P$ score) when isolating the contribution of the full FIG-MAC architecture.

\section{RQ Distribution Statistics}
\label{app:rq_distribution}

The 150 research questions are distributed as follows:

\begin{table}[h]
\centering
\small
\begin{tabular}{lcc}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{Percentage} \\
\midrule
\multicolumn{3}{l}{\textit{By Subfield}} \\
Natural Language Processing & 97 & 64.7\% \\
Computer Vision & 21 & 14.0\% \\
Reinforcement Learning & 19 & 12.7\% \\
Machine Learning (General) & 5 & 3.3\% \\
Knowledge Graphs & 5 & 3.3\% \\
Other & 3 & 2.0\% \\
\midrule
\multicolumn{3}{l}{\textit{By Difficulty}} \\
Beginner ($<$20 citations) & 95 & 63.3\% \\
Intermediate (20-100) & 45 & 30.0\% \\
Advanced ($>$100) & 10 & 6.7\% \\
\midrule
\multicolumn{3}{l}{\textit{By Year}} \\
2019--2020 & 27 & 18.0\% \\
2021--2022 & 60 & 40.0\% \\
2023--2024 & 63 & 42.0\% \\
\bottomrule
\end{tabular}
\caption{Distribution of the 150 research questions across subfields, difficulty levels, and publication years.}
\label{tab:rq_distribution}
\end{table}



\section{Semantic Unit Extraction Prompts}
\label{app:semantic_prompts}

Table~\ref{tab:semantic_prompt_extraction} presents the detailed prompts used for extracting semantic units from academic papers during the Fine-grained Inspiration Graph construction phase.

\begin{table}[h]
\centering
\setlength\tabcolsep{6pt}
\renewcommand{\arraystretch}{1.4}
\small
\begin{tabular}{p{3.5cm}p{9.5cm}}
\toprule
\textbf{Semantic Unit} & \textbf{Prompt (Extraction Requirements)} \\
\midrule
Core Problem & The single most important research question the paper focuses on; expressed concisely in 1-2 general, problem-oriented questions (e.g., 'How...?', 'Is it possible to...?') without technical details. \\
\midrule
Related Work & Summary of prior research ($\geq$200 words, third-person only) covering existing methods, advantages/disadvantages, research gaps; strictly excludes any reference to the current paper's content; emphasizes trends/limitations in literature. \\
\midrule
Preliminary Innovation Analysis & Analyze the proposed framework: list innovative modules (format: 'Module X: [Name] - [Function/novelty]') and framework-level innovations (if any); mandatory before generating Research Questions. \\
\midrule
Research Questions (RQ) & 2-4 distinct technical questions aligned 1-to-1 with identified innovations; each is a novel/difficult challenge, phrased concisely; non-redundant, quality over quantity. \\
\midrule
Simplified Research Question & Keyword-rich, searchable version of the corresponding RQ; retains core technical terms, omits full grammar; maximizes uniqueness for academic search engines. \\
\midrule
Solution (for Each RQ) & Detailed step-by-step explanation of how the paper addresses the RQ; includes full procedure, component interactions, definitions of abbreviations/coined terms; technically specific, no vague descriptions. \\
\midrule
Simplified Solution & Condensed, keyword-focused version of the corresponding Solution; includes key module names/algorithms; retains high-identifiability technical phrases. \\
\midrule
Framework Summary & 200-300+ word structured overview of the full method: design motivation, component roles, interactions, key strategies, unique value vs. prior work; uses clear organizational expressions (e.g., 'The framework includes...'). \\
\bottomrule
\end{tabular}
\caption{Core Semantic Unit Types and Corresponding Extraction Prompts. The table lists 8 primary semantic unit \textit{types}. In practice, each paper is parsed into 21 semantic unit \textit{instances}: including metadata attributes (DOI, title, authors, year, conference, venue, citation count, abstract), multiple research questions (RQ 1--4) and their simplified versions, multiple solutions (SOL 1--4) and their simplified versions, and the framework summary.}
\label{tab:semantic_prompt_extraction}
\end{table}


\section{Complete Baseline Configurations}
\label{app:baseline_config}

Table~\ref{tab:baseline_configs} summarizes the key configurations of baseline methods used in our comparative experiments.

\begin{table}[h]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lp{4cm}p{6cm}}
\toprule
\textbf{Baseline} & \textbf{Key Components} & \textbf{Configuration} \\
\midrule
\multirow{3}{*}{Virtual Scientists} 
 & Agent Architecture & 5 specialized agents (Leader, Researcher, Creative, Critic, Editor) with round-robin discussion \\
 & Knowledge Source & Semantic Scholar API + vector retrieval with top-k=10 \\
 & Discussion Rounds & 3 rounds of iterative refinement with majority voting \\
\midrule
\multirow{3}{*}{AI Scientist-v2} 
 & Search Strategy & Beam search with breadth-first tree expansion, branching factor=3 \\
 & Experimentation & Automated code generation and execution in sandboxed environment \\
 & Max Iterations & 10 iterations per hypothesis branch, early stopping on convergence \\
\midrule
\multirow{3}{*}{CoI-Agent} 
 & Chain Structure & Linear chain-of-ideas with 5 evolutionary steps \\
 & Innovation Mode & Evolutionary mutation + combinatorial fusion of idea pairs \\
 & Feedback Loop & Single-pass generation without iterative revision \\
\bottomrule
\end{tabular}
\caption{Baseline Method Configurations.}
\label{tab:baseline_configs}
\end{table}

\textbf{Fair Comparison Controls.} To ensure equitable evaluation across methods, we implement the following controls: (1) \textit{Knowledge Source}: All RAG-based methods (Virtual Scientists, CoI-Agent, FIG-MAC) access the same FAISS vector database (26,917 papers) and FIG knowledge graph (when applicable); (2) \textit{API Budget}: Each method is allocated equivalent LLM API call budgets (FIG-MAC uses $\sim$15 calls per RQ; baselines are configured to match this budget); (3) \textit{Backbone LLM}: All methods use the same backbone (Qwen-Max, Mixtral-8x7b, or LLaMA3.1-70b) for fair capability comparison; (4) \textit{Hyperparameter Tuning}: Baselines use their published default configurations; where defaults are unavailable, we perform grid search on the same validation set (50 RQs) used for FIG-MAC.

AI Scientist-v2 differs fundamentally as a non-RAG method that performs automated experimentation; thus, it lacks P and U$_{\text{src}}$ metrics by design. We report its N/A values to indicate metric inapplicability rather than implementation failure.


\section{Complete Agent Role Definitions and Prompts}
\label{app:agent_prompts}

\subsection{Agent Architecture Overview}

FIG-MAC comprises 8 specialized agents organized in a state-machine workflow. Table~\ref{tab:agent_roles} summarizes the agent roles and responsibilities.

\begin{table}[h]
\centering
\small
\begin{tabular}{llp{6cm}}
\toprule
\textbf{Agent Name} & \textbf{Role Type} & \textbf{Primary Responsibilities} \\
\midrule
Scholar Scour & Research Assistant & Literature review, evidence gathering, gap identification \\
Idea Igniter & Innovator & Creative hypothesis generation, cross-domain synthesis \\
Dr. Qwen Technical & Technical Reviewer & Technical feasibility, algorithmic complexity assessment \\
Dr. Qwen Practical & Practical Reviewer & Experimental design, resource estimation, timeline planning \\
Prof. Qwen Ethics & Ethical Reviewer & Ethical implications, societal impact, risk assessment \\
Dr. Qwen Leader & Coordinator & Synthesis integration, report writing, revision management \\
Critic Crucible & Quality Controller & Peer review, quality scoring, improvement suggestions \\
Prof. Qwen Editor & Editor & Final polishing, formatting, LaTeX compliance \\
\bottomrule
\end{tabular}
\caption{Agent Roles and Responsibilities.}
\label{tab:agent_roles}
\end{table}

\subsection{Agent 1: Scholar Scour (Literature Review)}

\begin{verbatim}
You are Scholar Scour, a Strategic AI4Science Researcher conducting 
a systematic review.

## Your Goal:
To excavate the Theoretical Foundations and Critical Gaps that will 
enable a Best Paper Award-winning hypothesis. You are not just 
summarizing; you are scouting for the next paradigm shift.

## Your Task:
Conduct a comprehensive literature review on the provided research 
topic, identifying state-of-the-art, key challenges, and promising 
directions. Output in structured Markdown format.

## Requirements:
1. Evidence Integration: Prioritize RAG Evidence, supplement with 
   your knowledge, use search tools for recent information
2. Established Knowledge: Identify 3-5 key consensus findings, 
   dominant theories, and foundational work
3. Knowledge Gaps: Pinpoint critical unanswered questions, 
   controversies, and research limitations
4. Promising Directions: Propose 2-3 research directions with 
   rationale and feasibility assessment

## Output Format:
# Literature Review: [Topic Title]

## Theoretical Foundations (The Roots)
[Identify core theories dominating the field]
- Key Papers: [Cite from RAG]

## Established Knowledge (The Branches)
### Finding N: [Concise Title]
- Description, Confidence Level, Evidence Strength, Key Sources

## The Critical Gap (The Opportunity)
### Gap N: [Concise Title]
- Description, Why it matters, Root Cause

## Promising Research Directions
### Direction N: [Concise Title]
- Rationale, Feasibility, Expected Impact

## Key References
1. (Authors, Year) Title. Venue. - Relevance, Contribution

## Synthesis Quality Assessment
- Evidence Sources Used, Overall Quality
\end{verbatim}

\subsection{Agent 2: Idea Igniter (Creative Generation)}

\begin{verbatim}
You are Idea Igniter, an Ambitious AI4Science Scientist aiming for 
a Best Paper Award at top venues (Nature, Science, NeurIPS, ICLR).

## Your Core Persona:
- Deep Thinker: You understand underlying mathematical and physical 
  principles, not just combining keywords
- Radical Visionary: You challenge fundamental assumptions
- Value-Driven: You care about IMPACT

## Your Task:
Generate 3-5 Groundbreaking Research Ideas using Hybrid Innovation:
- Path A: Deep Radical Innovation - New mechanism from first principles
- Path B: High-Value Combinatorial Innovation - Fuse fine-grained 
  details from retrieved papers

## Output Format (per idea):
### Idea N: [Concise, High-Impact Title]

**1. The 'Spark' (Core Concept):**
[2-3 sentences. Radical New Theory or Clever Synthesis?]

**2. The 'Gap' & 'Why Now?':**
[Why hasn't this been done? Cite limitations from RAG]

**3. The 'Twist' (Novelty & Depth):**
[What makes this deep?]

**4. Scientific Value:**
[Why does this matter?]

**5. Research Approach:**
- Variables, Method, Baselines, Expected Outcome, Challenge

**6. Testable Predictions:**
[Quantitative targets]

**7. Potential Impact:**
[Advancement to the field]

## Quality Standards:
- Specific technical terminology
- Feasible within 2-5 years
- Depth over Breadth
- Traceability: cite source papers
- Ambition: Aim for paradigm shift
\end{verbatim}

\subsection{Agent 3: Dr. Qwen Technical (Technical Review)}

\begin{verbatim}
You are Dr. Qwen Technical, an expert in theoretical sciences and 
technical feasibility assessment.

## Your Task:
Analyze creative ideas for technical soundness, implementation 
complexity, and resource requirements.

## Requirements:
1. Technical Plausibility: Theoretical foundation, logical 
   consistency, prior art, mathematical soundness
2. Implementation Complexity: Algorithmic complexity (O-notation), 
   system architecture, scalability, engineering challenges
3. Technical Risks: High-risk components, mitigation strategies, 
   alternative approaches
4. Resource Requirements: Expertise, computational resources, 
   timeline, dependencies

## Output Format:
# Technical Analysis

## Idea N: [One-sentence Summary]

### Technical Plausibility (Score: X/10)
- Theoretical Foundation, Logical Consistency, Prior Art, 
  Mathematical Soundness

### Implementation Complexity (Score: X/10)
- Algorithmic Complexity, System Architecture, Scalability, 
  Engineering Challenges

### Technical Risks
- High Risks, Mitigation Strategies, Alternative Approaches

### Required Resources
- Expertise, Computational Resources, Timeline, Dependencies

### Overall Assessment
- Overall Technical Score: X/10
- Innovation Level: X/10
- Potential Challenges
\end{verbatim}

\subsection{Agent 4: Dr. Qwen Practical (Practical Review)}

\begin{verbatim}
You are Dr. Qwen Practical, an expert in experimental science and 
practical implementation.

## Your Task:
Analyze creative ideas for practical feasibility, experimental 
viability, and real-world applicability.

## Requirements:
1. Falsifiability & Experimental Design: Testability, measurability, 
   observability, reproducibility; experiment design and data collection
2. Resource Requirements: Budget breakdown (equipment, personnel, 
   materials, overhead), team composition, equipment needs
3. Timeline & Risk Management: Project phases, milestones, critical 
   path; obstacles, mitigation solutions, contingency plans
4. Real-World Applicability: Equipment availability, ethical 
   constraints, practical deployment challenges

## Output Format:
# Practical Feasibility Analysis

## Idea N: [One-sentence Summary]

### Falsifiability & Testability (Score: X/10)
- Testability, Measurability, Observability, Reproducibility

### Experimental Feasibility (Score: X/10)
- Experiment Design, Data Collection, Equipment Availability, 
  Ethical Constraints

### Resource Requirements
- Budget: Equipment, Personnel, Materials, Overhead, Total Estimate
- Personnel: Roles, Expertise, Time commitment
- Equipment: Specifications and requirements
- Materials: Details and quantities

### Timeline
- Phases: Name, Duration, Goals, Deliverables
- Key Milestones
- Total Duration, Critical Path

### Risk Management
- Implementation Obstacles
- Mitigation Solutions
- Contingency Plans

### Overall Assessment
- Overall Practical Score: X/10
- Real-World Applications
- Implementation Readiness
\end{verbatim}

\subsection{Agent 5: Prof. Qwen Ethics (Ethical Review)}

\begin{verbatim}
You are Prof. Qwen Ethics, an expert in scientific ethics and 
societal impact assessment.

## Your Task:
Analyze creative ideas for ethical implications and societal impact.

## Requirements:
1. Research Ethics: Human/animal risks, data privacy, informed 
   consent, conflicts of interest, research integrity
2. Societal Impact: Beneficial uses, potential misuse, equity/access, 
   long-term consequences, environmental impact
3. Responsibility & Governance: Accountability, regulatory 
   compliance, stakeholder engagement, transparency
4. Multi-Dimensional Scoring: 1-10 scale for each dimension plus 
   overall score

## Output Format:
# Ethical & Societal Impact Analysis

## Idea N: [One-sentence Summary]

### Research Ethics (Score: X/10)
- Human/Animal Risks, Data Privacy, Informed Consent, 
  Conflicts of Interest, Research Integrity

### Societal Impact (Score: X/10)
- Beneficial Applications
- Potential Misuse
- Equity & Access
- Long-term Consequences
- Environmental Impact

### Responsibility & Governance (Score: X/10)
- Accountability, Regulatory Compliance, Stakeholder Engagement, 
  Transparency

### Overall Assessment
- Overall Ethics Score: X/10
- Critical Concerns
- Required Safeguards
- Recommendations
\end{verbatim}

\subsection{Agent 6: Dr. Qwen Leader (Synthesis and Revision)}

\begin{verbatim}
You are Dr. Qwen Leader, the Chief Researcher and Lead Author of 
a top-tier scientific paper.

## Your Goal:
Synthesize all inputs into a publication-ready scientific hypothesis 
report that is novel, rigorous, and impactful.

## ABSOLUTE REQUIREMENTS:
1. YOU ARE THE AUTHOR: Write in single, professional, authoritative 
   voice. No 'Agent X suggested...'
2. NO TRACES OF PROCESS: Final output must NOT contain process 
   markers or metadata
3. SYNTHESIZE: Internalize all inputs and rewrite them
4. INTEGRATE AND SYNTHESIZE: Analyze ALL ideas and synthesize best 
   elements from multiple ideas into unified, stronger hypothesis
5. STRICT LATEX FORMATTING:
   - Inline math: $E = mc^2$
   - Display math: $$\sum_{i=1}^n x_i$$
   - Output \sigma, \alpha directly (NOT \\sigma)

## YOUR CORE CAPABILITIES:

### 1. SYNTHESIZE (Initial Report Creation)
- Input: Literature reviews, creative ideas, multi-faceted analysis
- Task: Select BEST idea and write full hypothesis report
- Goal: 'This report must be accepted by Nature/Science/NeurIPS'

### 2. REVISE (Substantive Improvement)
- Input: Current draft + Critical feedback from Critic Crucible
- Task: Make SUBSTANTIVE changes, not cosmetic rewrites
- Revision Principles:
  - NEW CONTENT > REPHRASING: Add equations, algorithms, datasets
  - ADDRESS ROOT CAUSE: If 'lack of novelty', add new mechanisms
  - QUANTIFIABLE IMPROVEMENTS: Every revision adds 3-5 technical elements

### 3. FINALIZE (Quality Assurance)
- Ensure ALL sections present and complete
- Verify LaTeX formatting correct
- Confirm narrative flows: Gap -> Hypothesis -> Solution

## STANDARD REPORT FORMAT:

## Executive Summary
[2-3 sentences with strong Hook]

## Background and Rationale  
[Compelling narrative leading to hypothesis]

## Detailed Hypothesis
[Precise statement, key variables, testable predictions]

### Core Mechanism
[Key components, interactions, LaTeX formulations]

### Technical Innovations
[3-5 specific innovations with novelty explanation]

### Testable Predictions
[3-5 concrete, falsifiable predictions with metrics]

## Supporting Analysis
[Unified argument for plausibility and importance]

## Methodology
[Specific experimental approach, datasets, baselines]

## Expected Outcomes
[Predicted results and implications]

## Limitations & Future Directions
[Thoughtful constraints and actionable next steps]
\end{verbatim}

\subsection{Agent 7: Critic Crucible (Quality Review)}

\begin{verbatim}
You are Critic Crucible, a Senior Reviewer for a top-tier journal 
(e.g., Nature, Science, NeurIPS).

## Your Persona:
- Extremely hard to please. You only accept the top 1%.
- You HATE incremental improvements.
- You LOVE paradigm shifts, rigorous logic, surprising connections.
- Your goal is to REJECT any work that is flawed, derivative, or boring.

## Your Task:
Provide comprehensive peer review with specific, actionable 
improvement suggestions in structured Markdown format.

## Requirements:
1. Identify Strengths & Weaknesses: Cite specific technical details
2. Provide Detailed Improvements: Issue, solution, implementation 
   steps, expected impact, technical details
3. Assess Missing Elements: Specify what critical components are absent
4. Evaluate Quality Dimensions: Score novelty, rigor, feasibility, 
   clarity on 1-10 scale
5. Provide Overall Quality Score: Numeric score 1-10

## Output Format:

# Critical Analysis of [Topic]

## Overall Assessment
- Quality Score: X/10
- Recommendation: Accept / Revise / Reject
- Reasoning: [Justification. Be direct.]

## Strengths (Why this might be accepted)
- Strength 1, Strength 2, ...

## Weaknesses (Why I want to reject this)
- Weakness 1, Weakness 2, ...

## Critical Concerns (Showstoppers)
[Most important concerns]

## Detailed Improvement Suggestions (How to save this paper)

#### Suggestion N: [Issue Title]
- Issue: [Specific problem]
- Suggestion: [Actionable solution]
- Implementation: [Concrete steps]
- Impact: [Expected improvement]
- Technical Details: [Specific algorithms, methods, references]

[Repeat for 5-8 suggestions if score < 9]

## Missing Elements
- Element 1, Element 2, ...

## Quality Dimensions
- Technical Soundness: X/10
- Novelty Assessment: X/10
- Feasibility: X/10
- Clarity: X/10
\end{verbatim}

\subsection{Agent 8: Prof. Qwen Editor (Final Polish)}

\begin{verbatim}
You are Prof. Qwen Editor, a distinguished scientific editor at 
a top-tier publisher (e.g., Nature Publishing Group).

## Your Goal:
Transform a scientifically sound draft into a compelling, elegant, 
and high-impact manuscript. You elevate the narrative.

## Core Capabilities:

### Mode 1: Content Editor (Structural Improvements)
Use when review indicates:
- Structural issues (reorganize sections)
- Missing content (add baselines, protocols)
- Logic gaps (unclear connections)

Actions:
- Reorganize paragraphs and sections
- Add transition sentences
- Strengthen argumentation
- Expand brief sections

### Mode 2: Language Editor (Polishing)
Use when content is solid but needs refinement:
- Grammar and punctuation errors
- Awkward phrasing or wordiness
- Inconsistent terminology
- Tone inconsistencies

Actions:
- Fix grammatical errors
- Improve sentence flow
- Ensure consistent academic tone
- Perfect LaTeX formatting

## ABSOLUTE REQUIREMENTS:

1. OUTPUT ONLY THE POLISHED DOCUMENT: No editorial analysis, 
   scores, or recommendations in final output

2. PRESERVE ALL CONTENT: Do NOT remove sections, equations, 
   or citations. Improve, don't delete.

3. MAINTAIN SCIENTIFIC ACCURACY: Don't change technical meaning. 
   If unclear, improve explanation.

4. STRICT LATEX FORMATTING:
   - Inline math: $E = mc^2$
   - Display math: $$\sum_{{i=1}}^n x_i$$
   - Output \sigma, \alpha directly

## Editing Checklist (Complete ALL):
- [ ] All sections preserved
- [ ] Grammar and punctuation correct
- [ ] LaTeX equations render properly
- [ ] Terminology consistent
- [ ] Narrative flows: Gap -> Hypothesis -> Solution
- [ ] Tone authoritative and professional
- [ ] No process markers remain

## REMEMBER:
Your output is the FINAL version that will be saved and evaluated. 
Make it publication-ready.
\end{verbatim}


\section{Complete Workflow State Machine Configuration}
\label{app:workflow_config}

The multi-agent workflow is defined by a YAML configuration specifying state transitions, agent assignments, and quality gates. Table~\ref{tab:state_transitions} summarizes the state transition rules.

\begin{table}[h]
\centering
\small
\begin{tabular}{llp{6cm}}
\toprule
\textbf{Current State} & \textbf{Next State} & \textbf{Transition Condition} \\
\midrule
INIT & LITERATURE & Always \\
LITERATURE & IDEATION & Literature review complete ($\geq$10 papers) \\
IDEATION & ANALYSIS & Hypothesis draft complete \\
ANALYSIS & SYNTHESIS & All 3 parallel reviewers complete \\
SYNTHESIS & REVIEW & Synthesis document ready \\
REVIEW & POLISH & Quality score $\geq$ 8.0 or iteration $\geq$ 3 \\
REVIEW & REVISION & Quality score $<$ 8.0 and iteration $<$ 3 \\
REVISION & REVIEW & Revision complete \\
POLISH & FINISH & Final output formatted \\
\bottomrule
\end{tabular}
\caption{State Transition Rules.}
\label{tab:state_transitions}
\end{table}

\subsection{Complete Workflow YAML Configuration}

\begin{verbatim}
# Scientific Hypothesis Generation Workflow Configuration
# Based on HypothesisTeam state machine design

workflow:
  name: 'Scientific Hypothesis Generation Workflow'
  description: '8-agent collaborative scientific hypothesis generation'
  version: '2.0'

# Workflow state definitions
states:
  - name: 'INIT'
    display_name: 'Initialization'
    description: 'Initialize team and clear previous results'
    agents: []
    parallel: false
    required: true
    
  - name: 'LITERATURE'
    display_name: 'Literature Review'
    description: 'Literature review by Scholar Scour'
    agents: ['Scholar Scour']
    parallel: false
    required: true
    timeout: 300  # 5 minutes
    
  - name: 'IDEATION'
    display_name: 'Creative Ideation'
    description: 'Hypothesis generation by Idea Igniter'
    agents: ['Idea Igniter']
    parallel: false
    required: true
    timeout: 300
    
  - name: 'ANALYSIS'
    display_name: 'Parallel Analysis'
    description: 'Parallel review by 3 analysis agents'
    agents: ['Dr. Qwen Technical', 'Dr. Qwen Practical', 
             'Prof. Qwen Ethics']
    parallel: true
    required: true
    timeout: 600  # 10 minutes
    
  - name: 'SYNTHESIS'
    display_name: 'Synthesis Integration'
    description: 'Report writing by Dr. Qwen Leader'
    agents: ['Dr. Qwen Leader']
    parallel: false
    required: true
    timeout: 300
    
  - name: 'REVIEW'
    display_name: 'Peer Review'
    description: 'Quality control by Critic Crucible'
    agents: ['Critic Crucible']
    parallel: false
    required: true
    timeout: 300
    quality_check: true
    
  - name: 'REVISION'
    display_name: 'Iterative Revision'
    description: 'Revision by Dr. Qwen Leader'
    agents: ['Dr. Qwen Leader']
    parallel: false
    required: false
    timeout: 300
    iterative: true
    
  - name: 'POLISH'
    display_name: 'Final Polishing'
    description: 'Editing by Prof. Qwen Editor'
    agents: ['Prof. Qwen Editor']
    parallel: false
    required: true
    timeout: 300
    
  - name: 'FINISH'
    display_name: 'Completion'
    description: 'Workflow completion'
    agents: []
    parallel: false
    required: true

# State transition rules
transitions:
  INIT:
    - target: 'LITERATURE'
      condition: 'always'
      
  LITERATURE:
    - target: 'IDEATION'
      condition: 'success'
    - target: 'FINISH'
      condition: 'failure'
      
  IDEATION:
    - target: 'ANALYSIS'
      condition: 'success'
    - target: 'FINISH'
      condition: 'failure'
      
  ANALYSIS:
    - target: 'SYNTHESIS'
      condition: 'success'
    - target: 'FINISH'
      condition: 'failure'
      
  SYNTHESIS:
    - target: 'REVIEW'
      condition: 'success'
    - target: 'FINISH'
      condition: 'failure'
      
  REVIEW:
    - target: 'POLISH'
      condition: 'quality_threshold_met'
    - target: 'REVISION'
      condition: 'needs_improvement'
    - target: 'FINISH'
      condition: 'failure'
      
  REVISION:
    - target: 'REVIEW'
      condition: 'always'
      
  POLISH:
    - target: 'FINISH'
      condition: 'always'

# Global configuration
global_config:
  max_retries: 3
  default_timeout: 300
  enable_logging: true
  log_level: 'INFO'
  
  iteration:
    max_iterations: 3
    quality_threshold: 8.0  # 1-10 scale
    enable_iteration: true
    track_iteration_progress: true

# Error handling
error_handling:
  on_timeout: 'fail_state'
  on_agent_error: 'retry'
  max_state_retries: 2
  retry_delay: 10  # seconds
\end{verbatim}

\section{Complete List of 150 Research Questions}
\label{app:rq_list}

Table~\ref{tab:rq_statistics} presents the statistical distribution of the 150 research questions used in our evaluation.

\begin{table}[h]
\centering
\small
\caption{Distribution of 150 Research Questions.}
\label{tab:rq_statistics}
\begin{tabular}{lcc}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{Percentage} \\
\midrule
\multicolumn{3}{l}{\textit{By Conference}} \\
AAAI & 63 & 44.7\% \\
ACL & 31 & 22.0\% \\
EMNLP & 31 & 22.0\% \\
NAACL & 9 & 6.4\% \\
EACL & 7 & 5.0\% \\
\midrule
\multicolumn{3}{l}{\textit{By Year}} \\
2019 & 6 & 4.3\% \\
2020 & 14 & 9.9\% \\
2021 & 33 & 23.4\% \\
2022 & 27 & 19.1\% \\
2023 & 23 & 16.3\% \\
2024 & 38 & 27.0\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Research Question List}

Table~\ref{tab:rq_complete_list} presents the complete list of 150 research questions.

\footnotesize
\begin{longtable}{@{}p{0.5cm}p{7.2cm}p{2.5cm}@{}}
\caption{Complete List of 150 Research Questions.} \\
\label{tab:rq_complete_list} \\
\toprule
\textbf{ID} & \textbf{Research Question} & \textbf{Source} \\
\midrule
\endfirsthead
\multicolumn{3}{c}{\tablename\ \thetable{} -- Continued} \\
\toprule
\textbf{ID} & \textbf{Research Question} & \textbf{Source} \\
\midrule
\endhead
\midrule
\multicolumn{3}{r}{Continued on next page} \\
\endfoot
\bottomrule
\endlastfoot

1 & How can we integrate spatial crime dependencies with temporal dynamics to improve forecasting accuracy? & \texttt{10.1609/aaai.v36i4.20338} \\
2 & How can rules be iteratively refined using newly identified high-priority instances to adapt to evolving data distributions and improve long-term prioritization accuracy? & \texttt{10.1609/aaai.v33i01.33019440} \\
3 & How can pseudo-parallel data generated from structurally informative regions of the unmatched target KG improve the training of a collective relation integration model? & \texttt{10.18653/v1/2021.acl-long.363} \\
4 & How can gesture-enhanced handwriting be effectively combined with contextual insertion mechanics to support efficient deletion and modification of machine-translated text? & \texttt{10.18653/v1/2020.acl-main.155} \\
5 & How can we design a dynamic programming framework that uses ordered representatives to construct locally rainbow paths of bounded detour length? & \texttt{10.1609/aaai.v38i8.28639} \\
6 & How can adversarial text generation be designed to systematically evade deep sequence embedding-based classification models while maintaining semantic coherence and task-specific relevance? & \texttt{10.1609/aaai.v37i13.26811} \\
7 & How can aspect-opinion pairs be effectively represented in a domain-agnostic knowledge graph to capture their contextual sentiment relationships? & \texttt{10.1609/aaai.v36i11.21653} \\
8 & How can a claim verification system effectively integrate and reason over both textual and tabular information in long, hybrid-content financial documents? & \texttt{10.18653/v1/2024.emnlp-main.818} \\
9 & How can hierarchical graph structures be designed to expand concept representations with contextual information from knowledge graphs while preserving structural coherence? & \texttt{10.1609/aaai.v35i7.16796} \\
10 & How can question-answering systems systematically identify and differentiate between presuppositional and implicatural pragmatic inferences in health-related queries? & \texttt{10.18653/v1/2024.naacl-long.403} \\
11 & How can closed-form lower bounds for $\alpha$'(N,$\alpha$) be derived to enable fast calibration of NPSS without relying on computationally expensive randomization tests? & \texttt{10.1609/aaai.v36i4.20339} \\
12 & How can fault prediction models be enhanced with data augmentation techniques to improve the accuracy of software bug localization? & \texttt{10.1609/aaai.v33i01.33019446} \\
13 & How can multiple types of argumentation knowledge graphs be effectively combined to guide the generation of factually consistent and semantically rich arguments? & \texttt{10.18653/v1/2021.acl-long.366} \\
14 & How can a large-scale, domain-specific stance detection dataset for financial M\&A events be constructed with high inter-annotator reliability and balanced class distribution? & \texttt{10.18653/v1/2020.acl-main.157} \\
15 & How can a formula be decomposed into a unary function applied to a single parameter and a second function operating on the remaining inputs, enabling recursive isolation of structural components? & \texttt{10.1609/aaai.v38i8.28641} \\
16 & How can a deep learning-based pre-classifier effectively distinguish between normal and abnormal weld seam images to filter out invalid cases before detection? & \texttt{10.1609/aaai.v37i13.26834} \\
17 & How can graph-based link prediction be effectively integrated into cross-domain clustering to improve cluster quality? & \texttt{10.1609/aaai.v36i11.21654} \\
18 & How can a dual-stream architecture with adaptive fusion strategies improve the robustness of multimodal ASR by leveraging both vision hotword streams and traditional ASR outputs? & \texttt{10.18653/v1/2024.emnlp-main.821} \\
19 & How can pre-training strategies be adapted to effectively leverage knowledge graph structures for improving generalization to unseen concept sets in generative commonsense reasoning tasks? & \texttt{10.1609/aaai.v35i7.16796} \\
20 & How can regularization techniques be integrated into annotator embedding learning to prevent overfitting, especially for sparse or low-contribution annotators? & \texttt{10.18653/v1/2024.naacl-long.407} \\
21 & How can human annotation experiments be designed to systematically evaluate the differences between emotions expressed by writers and those perceived by readers, and what implications do these diff... & \texttt{10.18653/v1/2021.findings-emnlp.219} \\
22 & How can a prior over world-models be designed to favor models that assume the external world is static during an episode, thereby preventing an agent from forming plans that require long-term envir... & \texttt{10.1609/aaai.v34i03.5628} \\
23 & How can intra-diversity constraints be formulated to ensure generated solutions remain near-optimal while inter-diversity constraints enforce sufficient differences between solutions? & \texttt{10.1609/aaai.v34i02.5512} \\
24 & How can the numerical instability of the intersection matrix in skeleton decomposition be mitigated to improve approximation accuracy in self-attention? & \texttt{10.1609/aaai.v36i1.19962} \\
25 & How can adversarial perturbations be optimized to concentrate on dominant frequency regions that are consistently influential across different deep neural networks? & \texttt{10.1609/aaai.v38i6.28427} \\
26 & How can a high-quality textual relation embedding be learned using global co-occurrence statistics between textual and knowledge base relations as supervision? & \texttt{10.18653/v1/p19-1127} \\
27 & How does the scale of transformer language models (e.g., parameter count) influence their ability to process and adapt to atypical animacy, and what does this reveal about their internal representa... & \texttt{10.18653/v1/2023.emnlp-main.744} \\
28 & What is the optimal method for identifying the most relevant evidence sentence in an academic abstract that contains the answer to a given question? & \texttt{10.1609/aaai.v33i01.33019855} \\
29 & How can the ethical risks of NLP crowdsourcing tasks be systematically assessed using the Belmont Report's principles to ensure alignment with human-subjects research ethics? & \texttt{10.18653/v1/2021.naacl-main.295} \\
30 & How can range-null space decomposition be leveraged to enforce strict data consistency in multi-contrast MRI reconstruction while minimizing information loss? & \texttt{10.1609/aaai.v38i2.27869} \\
31 & How do model size, decoding strategies, and prompting with training data affect the novelty of LM-generated text? & \texttt{10.18653/v1/2024.emnlp-main.800} \\
32 & How can the integration of re-anchoring with auxiliary strategies like transfer learning and interactive attention further improve the robustness of implicit discourse relation classifiers? & \texttt{10.18653/v1/2021.findings-emnlp.110} \\
33 & How can spherical coordinate perturbation and pixelwise depth intervals be combined to refine normal and depth estimates in textureless regions? & \texttt{10.1609/aaai.v38i7.28512} \\
34 & How can a single adapter module be trained to adapt a multilingual NMT model to arbitrary new domains and language pairs without requiring domain- or language-specific parameter updates? & \texttt{10.18653/v1/2022.findings-emnlp.315} \\
35 & How can a multi-layer funnel pooling strategy in Conformer encoders achieve progressive frame rate reduction while maintaining sufficient temporal resolution for accurate speech recognition? & \texttt{10.18653/v1/2024.naacl-long.344} \\
36 & How can an integrated evaluation framework be designed to systematically assess multiple dimensions of metric quality, including correlation, generalization, robustness, and coherence judgment, in ... & \texttt{10.18653/v1/2021.acl-long.500} \\
37 & How can an online agent balance adherence to learned behavioral constraints with the need to maximize reward in a dynamic environment? & \texttt{10.1609/aaai.v33i01.33013} \\
38 & How can federated learning achieve group fairness through dynamic aggregation weight adjustment based on misalignment between local and global fairness metrics? & \texttt{10.1609/aaai.v37i6.25911} \\
39 & Can multilingual transformer models be effectively adapted for cross-lingual acceptability classification tasks, and what are the limitations of this approach for low-resource languages like Italian? & \texttt{10.18653/v1/2021.findings-emnlp.250} \\
40 & How can a domain-specific pre-training dataset for Vietnamese hate speech detection be automatically generated to capture the linguistic diversity and contextual complexity of social media content? & \texttt{10.18653/v1/2024.findings-acl.355} \\
41 & How can external biomedical knowledge graphs be integrated with AMR representations to improve the understanding of domain-specific entities and events? & \texttt{10.18653/v1/2021.acl-long.489} \\
42 & How can a utility function be modified to ensure robustness against (agent $\times$ item)-level differential privacy constraints while preserving fairness guarantees? & \texttt{10.1609/aaai.v37i5.25721} \\
43 & How can spatial and frequency domain information be effectively fused within a diffusion model to improve low-light image restoration quality? & \texttt{10.1609/aaai.v38i5.28273} \\
44 & How can a multi-task training strategy be implemented to jointly optimize hyper-relational KG embedding and contrastive learning objectives without degrading performance? & \texttt{10.18653/v1/2024.findings-acl.171} \\
45 & How can manifold learning be integrated with probabilistic modeling to prevent information loss and improve the accuracy of deformation distribution estimation? & \texttt{10.1609/aaai.v36i11.21637} \\
46 & How can we learn pose-invariant latent representations for single-view 3D reconstruction that are robust to variations in object orientation? & \texttt{10.1609/aaai.v36i1.19920} \\
47 & What is the effectiveness of a RoBERTa-based political stance classifier in identifying biased opinions within generated summaries? & \texttt{10.48550/arxiv.2402.00322} \\
48 & How can an adversarial training mechanism be designed to prevent the generator from relying on simple heuristics when producing entailment-aware paraphrases? & \texttt{10.1609/aaai.v36i10.21376} \\
49 & What is the impact of incorporating automatically generated affirmative interpretations into the input of pre-trained models for robustness against negation? & \texttt{10.18653/v1/2024.acl-short.55} \\
50 & How can a model-agnostic post-processing framework effectively integrate with diverse summarization models without requiring retraining? & \texttt{10.18653/v1/2024.findings-acl.59} \\
51 & Can feature-based interpretability methods produce significantly different attributions for functionally equivalent neural text classifiers with distinct random initializations? & \texttt{10.18653/v1/2021.findings-acl.327} \\
52 & How can feature importance be leveraged to avoid unnecessary reconstruction of unimportant features during pruning? & \texttt{10.1609/aaai.v34i07.6720} \\
53 & How can few-shot learning strategies be integrated with calibration techniques to further reduce miscalibration in Massively Multilingual Language Models (MMLMs) for languages with limited resources? & \texttt{10.18653/v1/2022.emnlp-main.290} \\
54 & How can the ReviewCritique dataset be utilized to benchmark the effectiveness of both closed-source and open-source LLMs in scientific peer review tasks? & \texttt{10.18653/v1/2024.emnlp-main.292} \\
55 & How can a query-based online search algorithm tolerate up to \$H\$ erroneous binary responses while efficiently narrowing down the optimal price range? & \texttt{10.1609/aaai.v36i9.21199} \\
56 & How can Contrastive Decoding be adapted to dynamically adjust its strength based on the confidence of the expert model to avoid degrading non-hallucinated translations? & \texttt{10.18653/v1/2024.eacl-long.155} \\
57 & How can channel-wise heterogeneous kernel replacement be designed to adaptively select complementary 1D/2D/3D sub-kernels for each channel in 3D networks? & \texttt{10.1609/aaai.v35i4.16433} \\
58 & How can the joint optimization of syntactic structure and visual-semantic alignment be achieved in an end-to-end unsupervised framework? & \texttt{10.18653/v1/n19-1180} \\
59 & What graph update mechanism can effectively capture both the relational structure of multi-party dialogues and the temporal evolution of emotional states? & \texttt{10.18653/v1/2022.acl-long.24} \\
60 & How can continuous topic-word distributions be sampled in a differentiable manner to enable end-to-end learning of sentiment-aware topics? & \texttt{10.18653/v1/2021.eacl-main.199} \\
61 & How can a generative adversarial network be adapted to produce high-quality, class-specific embeddings that enhance few-shot learning without memorizing training examples? & \texttt{10.18653/v1/2022.naacl-main.404} \\
62 & How can a shared Attention Residual Gaussian Distribution (ARGD) module enhance the integration of textual information into the posterior path of a variational autoencoder for sign language transla... & \texttt{10.1609/aaai.v38i17.29937} \\
63 & How can data augmentation techniques improve the generalization of Gin Rummy hand evaluation models trained on limited or biased datasets? & \texttt{10.1609/aaai.v35i17.17843} \\
64 & How can spatio-temporal dependencies in agricultural pricing and volume data be jointly modeled using dual temporal convolutional networks to improve prediction accuracy? & \texttt{10.1609/aaai.v34i08.7039} \\
65 & How can a multi-branch mixture density network effectively model the distribution of auction durations by combining game-theoretic predictions with product embeddings? & \texttt{10.1609/aaai.v38i9.28854} \\
66 & How can a multi-slot mechanism iteratively specialize variable representations to capture complex contextual dependencies in mathematical text? & \texttt{10.18653/v1/2022.findings-acl.76} \\
67 & What are the key structural properties of short clauses and low-occurrence variables that the adaptive branching rules exploit to achieve improved performance over prior methods? & \texttt{10.1609/aaai.v35i5.16479} \\
68 & How can a relation classifier be trained to produce confident predictions for individual sentences in an unsupervised setting? & \texttt{10.18653/v1/p19-1133} \\
69 & What evaluation metric can effectively measure the quality of predicted explanations by incorporating human judgments of intuitiveness, even when multiple valid explanations exist? & \texttt{10.1609/aaai.v36i11.21577} \\
70 & How can zero-shot translation capabilities of multilingual MT models be effectively repurposed for grammatical error correction without task-specific adaptation? & \texttt{10.18653/v1/2024.eacl-long.73} \\
71 & How can cell-level layout information be encoded to enable models to recognize semantically coherent units spanning multiple words within a single cell? & \texttt{10.18653/v1/2021.acl-long.493} \\
72 & How can the outputs of a pattern-exploitation module be integrated with dynamic context augmentation to improve cross-domain generalization in NED? & \texttt{10.18653/v1/2022.findings-emnlp.506} \\
73 & How can dialog systems effectively detect and respond to negative grounding signals (e.g., inconsistencies, errors) to enable collaborative error recovery? & \texttt{10.18653/v1/2021.eacl-main.41} \\
74 & How can a time series prediction model dynamically adapt to the distribution of extreme and normal values while maintaining robustness to imbalanced data? & \texttt{10.1609/aaai.v37i7.26045} \\
75 & How does subfamily-specific pretraining with custom tokenizers enhance model performance for low-resource languages compared to generic multilingual tokenization strategies? & \texttt{10.18653/v1/2023.findings-eacl.93} \\
76 & How can a shared expert mechanism with routing weight normalization be designed to address scale mismatch and improve the effectiveness of sparse upcycling in instruction-tuned code LLMs? & \texttt{10.18653/v1/2024.acl-long.699} \\
77 & How can a semantic latent space be identified and utilized for controllable, accumulative, and composable image editing in transformer-based Flow Matching models? & \texttt{10.1609/aaai.v38i3.27998} \\
78 & Can language models generalize monotonicity-based NPI licensing to unseen environments without explicit training on NPI occurrences? & \texttt{10.18653/v1/2021.findings-acl.439} \\
79 & How can classical optimization techniques be adapted to train quantum classifiers with high accuracy on real-world datasets? & \texttt{10.1609/aaai.v35i18.17941} \\
80 & How can an alternating optimization strategy ensure convergence in online pairwise learning without relying on buffer storage or i.i.d. assumptions? & \texttt{10.1609/aaai.v38i10.28955} \\
81 & How can NLP and ML research better integrate democratic theories to develop frameworks that ensure equitable participation, accountability, and alignment with democratic values in AI systems? & \texttt{10.18653/v1/2024.emnlp-main.184} \\
82 & How does pre-expansion pruning in trie-constrained decoding improve the accuracy and efficiency of parallel sentence retrieval compared to post-expansion pruning? & \texttt{10.18653/v1/2020.acl-main.152} \\
83 & How can transferable component prototypes for individual human-annotated attributes be learned and reused to construct compositional representations for novel classes? & \texttt{10.1609/aaai.v37i7.26082} \\
84 & How can Chinese characters be effectively transformed into a Latinized stroke sequence representation to leverage subword modeling techniques in NMT? & \texttt{10.18653/v1/2022.emnlp-main.434} \\
85 & How can a contrastive self-training framework with adaptive temperature control improve classification performance by balancing confidence and generalization in pseudo-label learning? & \texttt{10.18653/v1/2024.eacl-long.39} \\
86 & How can adversarial effectiveness in NMT be evaluated without relying on ground-truth reference translations? & \texttt{10.18653/v1/2021.acl-long.153} \\
87 & How can answer spans in paragraphs be leveraged to align answerable and unanswerable question pairs, ensuring both relevance and difficulty? & \texttt{10.18653/v1/n19-1415} \\
88 & How can motion conditions be efficiently mapped to tri-plane feature deformations without using 3D parametric models? & \texttt{10.1609/aaai.v38i7.28473} \\
89 & How can a TableQA benchmark be constructed to systematically evaluate robustness against diverse, human-annotated adversarial perturbations in table headers, content, and questions? & \texttt{10.18653/v1/2023.acl-long.334} \\
90 & How can an alternating optimization algorithm be designed to jointly estimate true labels and train DNN parameters in the presence of instance-dependent label noise? & \texttt{10.1609/aaai.v35i11.17221} \\
91 & How can sequential visual and positional features be adaptively fused to improve robustness in UAV navigation under dynamic environmental conditions? & \texttt{10.1609/aaai.v38i9.28906} \\
92 & How can latent temporal motion information be effectively predicted and encoded in still images for action recognition? & \texttt{10.1609/aaai.v34i03.5653} \\
93 & What architectural design or training strategy enables entity linking models to robustly handle NIL prediction without overfitting to non-NIL examples? & \texttt{10.18653/v1/2023.findings-acl.690} \\
94 & How can conversational patterns from the Natural Conversation Framework be systematically integrated into goal-oriented dialog datasets to reflect naturalistic user behavior? & \texttt{10.18653/v1/2020.findings-emnlp.358} \\
95 & How does the paper design a pre-training task for multi-hop retrievers that enables iterative document retrieval for sub-questions without requiring human annotations? & \texttt{10.18653/v1/2021.findings-acl.62} \\
96 & How can a model determine the optimal position to insert a simile into a given text to maximize contextual coherence? & \texttt{10.1609/aaai.v35i16.17691} \\
97 & How can we generate logically coherent answer-explanation pairs in VQA-NLE by modeling reasoning steps as a chain-of-thought process? & \texttt{10.1609/aaai.v38i3.28065} \\
98 & How can global property representations be adaptively fused with local sentence features to improve relation prediction? & \texttt{10.18653/v1/2022.findings-naacl.128} \\
99 & How can symptom status recognition be improved by formulating it as a natural language inference task that integrates both dialogue context and external medical knowledge? & \texttt{10.18653/v1/2023.findings-acl.652} \\
100 & How can the trade-off between attack transferability and stealthiness be dynamically controlled during adversarial perturbation generation in the latent space? & \texttt{10.1609/aaai.v38i4.28147} \\
101 & How can human annotation strategies be optimized to effectively evaluate the quality of contrastive explanations in NLP tasks? & \texttt{10.18653/v1/2023.emnlp-main.427} \\
102 & How can hard and soft constraints be effectively combined with pre-trained language models to guide high-quality constrained generation without task-specific training? & \texttt{10.18653/v1/2020.findings-emnlp.115} \\
103 & How can global label hierarchy be effectively encoded into label embeddings using a pre-trained language model without requiring auxiliary graph encoders or intentional fusion of hierarchical and s... & \texttt{10.18653/v1/2022.emnlp-main.268} \\
104 & How can low-performing or data-inefficient clients in federated learning be automatically identified and excluded to improve global model accuracy in autonomous driving simulations? & \texttt{10.1609/aaai.v37i13.26984} \\
105 & How can action and information flow relationships between sentences in procedural texts be inferred without explicit named entity recognition or domain-specific rules? & \texttt{10.18653/v1/2021.findings-acl.345} \\
106 & How can segmentation uncertainty be quantified and visualized through dynamically adjustable predictive regions that reflect user-specified confidence levels? & \texttt{10.1609/aaai.v37i13.26837} \\
107 & How can structured semantic representations for events and arguments be learned from text and visual data in a weakly supervised manner without requiring explicit cross-modal annotations? & \texttt{10.18653/v1/2020.acl-main.230} \\
108 & How do different architectural designs and pretraining objectives of pretrained language models affect their ability to capture and represent document-level discourse information across multiple la... & \texttt{10.18653/v1/2021.naacl-main.301} \\
109 & Does a text-based hate speech support set outperform a vision-language hate speech support set in few-shot in-context learning for cross-modal hate speech detection? & \texttt{10.18653/v1/2024.emnlp-main.445} \\
110 & How can non-autoregressive translation models be trained to progressively learn bilingual knowledge from fine-grained units (words/phrases) to full-sentence structures? & \texttt{10.18653/v1/2021.findings-acl.247} \\
111 & How can adversarial test cases be generated by systematically replacing answer-relevant spans in evidence with alternative answers while maintaining contextual coherence? & \texttt{10.18653/v1/2024.findings-naacl.85} \\
112 & How can adversarial training be adapted to improve zero-shot cross-lingual transfer by encouraging robustness to embedding misalignments in multilingual representations? & \texttt{10.18653/v1/2021.emnlp-main.126} \\
113 & How can the decoder be modified to interpret intermediate encoder representations in encoder-decoder Transformers? & \texttt{10.18653/v1/2024.findings-naacl.296} \\
114 & How can the integration of auxiliary tasks during the transition phase improve model stability and prevent catastrophic forgetting when shifting from formal to informal data? & \texttt{10.18653/v1/2020.findings-emnlp.282} \\
115 & How can dataset splits be redesigned to mitigate biases from source/time overlap and improve the reliability of evaluation metrics for unreliable news detection? & \texttt{10.18653/v1/2021.eacl-main.211} \\
116 & How can patch-level visual patterns from head classes be effectively transferred to tail classes through self-distillation to alleviate their under-representation? & \texttt{10.1609/aaai.v38i6.28459} \\
117 & How can a branch-and-bound algorithm be designed to iteratively reduce the relaxation gap of the enhanced SDP relaxation and converge to the exact solution? & \texttt{10.1609/aaai.v37i12.26745} \\
118 & How can a value tagger be used to filter noisy or semantically incorrect rewritten utterances in synthesized multi-domain dialogs? & \texttt{10.18653/v1/2023.emnlp-main.946} \\
119 & What methods can enable LLMs to engage in meaningful, multi-turn discussions or debates on abstract topics (e.g., philosophy, ethics) while maintaining coherence, avoiding contradictions, and refle... & \texttt{10.18653/v1/2023.emnlp-main.146} \\
120 & How can variational inference be adapted to the probabilistic CCA framework to efficiently approximate the posterior distribution of the shared latent variable and view-specific factors in a deep g... & \texttt{10.1609/aaai.v35i9.16982} \\
121 & How can a weakly supervised segmentation model be integrated into a detection framework to achieve pixel-level damage localization using only bounding box annotations? & \texttt{10.1609/aaai.v34i09.7110} \\
122 & How can a dual decoupling framework effectively separate clean and noisy pseudo boxes to improve training stability and performance in semi-supervised object detection? & \texttt{10.1609/aaai.v36i3.20264} \\
123 & How can a funnel-shaped neural network architecture be designed to achieve high compression efficiency while maintaining reconstruction fidelity for spectrum-concentrated data blocks? & \texttt{10.1609/aaai.v37i4.25602} \\
124 & How can instrumental variables be generated under unconditional moment restrictions to eliminate confounding effects in graph representation learning? & \texttt{10.1609/aaai.v37i6.25925} \\
125 & How can combining embeddings from both shallow and deep layers of a transformer model enhance sentence representation quality? & \texttt{10.18653/v1/2021.findings-emnlp.23} \\
126 & How can structured relational knowledge (from hyperlinks) and unstructured factual knowledge (from documents) be dynamically fused during retrieval to improve evidence selection? & \texttt{10.1609/aaai.v35i15.17568} \\
127 & How can the capacity of adapter modules be dynamically adjusted to balance performance gains and computational efficiency across tasks with varying data sizes or complexity? & \texttt{10.18653/v1/d19-1165} \\
128 & How can a multi-hop selection mechanism be designed to iteratively filter the most relevant context utterances for response matching in multi-turn conversations? & \texttt{10.18653/v1/d19-1011} \\
129 & How can symbolic search be combined with neural proof generation to explore diverse and valid proof paths in large search spaces? & \texttt{10.18653/v1/2022.emnlp-main.7} \\
130 & How does the hierarchical organization of discourse units, as defined by Rhetorical Structure Theory, influence the predictability of information density fluctuations? & \texttt{10.18653/v1/2024.emnlp-main.1047} \\
131 & How can relative position representations improve the modeling of long-range dependencies in source code summarization compared to absolute position encodings? & \texttt{10.18653/v1/2020.acl-main.449} \\
132 & How can graph neural networks be designed to efficiently encode high-order dependency relationships in a direction-aware manner? & \texttt{10.18653/v1/n19-1237} \\
133 & How can conditional gradients be adapted to enforce global convex constraints in deep neural networks while maintaining computational efficiency and convergence guarantees? & \texttt{10.1609/aaai.v33i01.33014772} \\
134 & How can uncertainty-aware contrastive learning be integrated into keypoint detection to improve robustness for texture-less or symmetric objects while maintaining semantic consistency? & \texttt{10.1609/aaai.v36i5.20482} \\
135 & How can local correlation analysis of counterfactual examples be used to disentangle syntactic influences from distributional biases in nationality-related name effects? & \texttt{10.18653/v1/2024.emnlp-main.34} \\
136 & What treebank selection strategy maximizes parsing performance for low-resource languages by combining training data size and linguistic similarity metrics in an automated, heuristic-driven manner? & \texttt{10.18653/v1/2021.findings-acl.431} \\
137 & What automated methods can effectively standardize and annotate complex legal elements (e.g., charges, law articles, penalties) in multi-defendant cases? & \texttt{10.18653/v1/2024.findings-acl.351} \\
138 & How can the teaching order of multiple aligners in a cycle-teaching framework be dynamically optimized to maximize overall performance and minimize error propagation? & \texttt{10.1609/aaai.v36i4.20348} \\
139 & How can a QA system perform compositional reasoning over complex, logically structured documents to identify answers that depend on conjunctions, disjunctions, or exceptions in the text? & \texttt{10.18653/v1/2022.acl-long.253} \\
140 & What is the effectiveness of combining intra-layer self-similarity and inter-layer linear CKA similarity in detecting overfitting of rare and minority group names in neural language models? & \texttt{10.18653/v1/2021.emnlp-main.41} \\
141 & What methods can be used to collect and represent high-quality, diverse annotations from multiple annotators while minimizing bias and ensuring reliability? & \texttt{10.1609/aaai.v37i6.25840} \\
142 & How can the computational efficiency of inference-based filtering be maintained while ensuring high-quality, coherent story outputs? & \texttt{10.18653/v1/2022.findings-emnlp.520} \\
143 & Can the linear optimization problem over the convex polytope \$ C\_\{p\textasciicircum{}\{n+2\}\} \$ be proven \#P-hard, and how does this relate to the verification of semivalues for linear thresh... & \texttt{10.1609/aaai.v33i01.33011869} \\
144 & How can multiple distance metrics be combined into a unified loss function to improve cross-lingual alignment performance across diverse language pairs? & \texttt{10.18653/v1/2021.findings-acl.276} \\
145 & How can source-side information be utilized to improve the retrieval of relevant examples in kNN-MT? & \texttt{10.18653/v1/2023.emnlp-main.503} \\
146 & How can high-quality hard negative samples be generated in the embedding space to improve the discriminative power of contrastive learning for time series? & \texttt{10.1609/aaai.v38i12.29299} \\
147 & How can intra-document structural information be utilized to improve the robustness of contrastive learning models against length-induced semantic drift? & \texttt{10.18653/v1/2023.emnlp-main.86} \\
148 & How can a collaborative framework integrate panoptic-level selection with region-based refinement to achieve efficient and effective active learning for semantic segmentation? & \texttt{10.1609/aaai.v36i2.20107} \\
149 & How can semi-factual data generated using human-identified rationales improve model robustness in few-shot learning without requiring extensive manual intervention? & \texttt{10.18653/v1/2022.acl-long.481} \\
150 & How can a scoring mechanism be designed to prioritize functional correctness by emphasizing recall over precision in evaluating code generation quality? & \texttt{10.18653/v1/2023.emnlp-main.859} \\
\end{longtable}


\end{document}
