

\section{Complete List of 150 Research Questions}
\label{app:rq_list}

Table~\ref{tab:rq_statistics} presents the statistical distribution of the 150 research questions used in our evaluation.

\begin{table}[h]
\centering
\small
\caption{Distribution of 150 Research Questions.}
\label{tab:rq_statistics}
\begin{tabular}{lcc}
\toprule
\textbf{Category} & \textbf{Count} & \textbf{Percentage} \\
\midrule
\multicolumn{3}{l}{\textit{By Conference}} \\
AAAI & 63 & 42.0\% \\
ACL & 33 & 22.0\% \\
EMNLP & 33 & 22.0\% \\
NAACL & 12 & 8.0\% \\
EACL & 9 & 6.0\% \\
\midrule
\multicolumn{3}{l}{\textit{By Year}} \\
2019 & 13 & 8.7\% \\
2020 & 14 & 9.3\% \\
2021 & 33 & 22.0\% \\
2022 & 27 & 18.0\% \\
2023 & 23 & 15.3\% \\
2024 & 40 & 26.7\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Research Question List}

Table~\ref{tab:rq_complete_list} presents the complete list of 150 research questions.

\footnotesize
\begin{longtable}{@{}p{0.5cm}p{7.2cm}p{2.5cm}@{}}
\caption{Complete List of 150 Research Questions.} \\
\toprule
\textbf{ID} & \textbf{Research Question} & \textbf{Source} \\
\midrule
\endfirsthead
\multicolumn{3}{c}{\tablename\ \thetable{} -- Continued} \\
\toprule
\textbf{ID} & \textbf{Research Question} & \textbf{Source} \\
\midrule
\endhead
\midrule
\multicolumn{3}{r}{Continued on next page} \\
\endfoot
\bottomrule
\endlastfoot

1 & How can we integrate spatial crime dependencies with temporal dynamics to improve forecasting accuracy? & \cite{10.1609/aaai.v36i4.20338} \\
2 & How can rules be iteratively refined using newly identified high-priority instances to adapt to evolving data distributions and improve long-term prioritization accuracy? & \cite{10.1609/aaai.v33i01.33019440} \\
3 & How can pseudo-parallel data generated from structurally informative regions of the unmatched target KG improve the training of a collective relation integration model? & \cite{10.18653/v1/2021.acl-long.363} \\
4 & How can gesture-enhanced handwriting be effectively combined with contextual insertion mechanics to support efficient deletion and modification of machine-translated text? & \cite{10.18653/v1/2020.acl-main.155} \\
5 & How can we design a dynamic programming framework that uses ordered representatives to construct locally rainbow paths of bounded detour length? & \cite{10.1609/aaai.v38i8.28639} \\
6 & How can adversarial text generation be designed to systematically evade deep sequence embedding-based classification models while maintaining semantic coherence and task-specific relevance? & \cite{10.1609/aaai.v37i13.26811} \\
7 & How can aspect-opinion pairs be effectively represented in a domain-agnostic knowledge graph to capture their contextual sentiment relationships? & \cite{10.1609/aaai.v36i11.21653} \\
8 & How can a claim verification system effectively integrate and reason over both textual and tabular information in long, hybrid-content financial documents? & \cite{10.18653/v1/2024.emnlp-main.818} \\
9 & How can hierarchical graph structures be designed to expand concept representations with contextual information from knowledge graphs while preserving structural coherence? & \cite{10.1609/aaai.v35i7.16796} \\
10 & How can question-answering systems systematically identify and differentiate between presuppositional and implicatural pragmatic inferences in health-related queries? & \cite{10.18653/v1/2024.naacl-long.403} \\
11 & How can closed-form lower bounds for α′(N,α) be derived to enable fast calibration of NPSS without relying on computationally expensive randomization tests? & \cite{10.1609/aaai.v36i4.20339} \\
12 & How can fault prediction models be enhanced with data augmentation techniques to improve the accuracy of software bug localization? & \cite{10.1609/aaai.v33i01.33019446} \\
13 & How can multiple types of argumentation knowledge graphs be effectively combined to guide the generation of factually consistent and semantically rich arguments? & \cite{10.18653/v1/2021.acl-long.366} \\
14 & How can a large-scale, domain-specific stance detection dataset for financial M\&A events be constructed with high inter-annotator reliability and balanced class distribution? & \cite{10.18653/v1/2020.acl-main.157} \\
15 & How can a formula be decomposed into a unary function applied to a single parameter and a second function operating on the remaining inputs, enabling recursive isolation of structural components? & \cite{10.1609/aaai.v38i8.28641} \\
16 & How can a deep learning-based pre-classifier effectively distinguish between normal and abnormal weld seam images to filter out invalid cases before detection? & \cite{10.1609/aaai.v37i13.26834} \\
17 & How can graph-based link prediction be effectively integrated into cross-domain clustering to improve cluster quality? & \cite{10.1609/aaai.v36i11.21654} \\
18 & How can a dual-stream architecture with adaptive fusion strategies improve the robustness of multimodal ASR by leveraging both vision hotword streams and traditional ASR outputs? & \cite{10.18653/v1/2024.emnlp-main.821} \\
19 & How can pre-training strategies be adapted to effectively leverage knowledge graph structures for improving generalization to unseen concept sets in generative commonsense reasoning tasks? & \cite{10.1609/aaai.v35i7.16796} \\
20 & How can regularization techniques be integrated into annotator embedding learning to prevent overfitting, especially for sparse or low-contribution annotators? & \cite{10.18653/v1/2024.naacl-long.407} \\
21 & How can human annotation experiments be designed to systematically evaluate the differences between emotions expressed by writers and those perceived by readers, and what implications do these diff... & \cite{10.18653/v1/2021.findings-emnlp.219} \\
22 & How can a prior over world-models be designed to favor models that assume the external world is static during an episode, thereby preventing an agent from forming plans that require long-term envir... & \cite{10.1609/aaai.v34i03.5628} \\
23 & How can intra-diversity constraints be formulated to ensure generated solutions remain near-optimal while inter-diversity constraints enforce sufficient differences between solutions? & \cite{10.1609/aaai.v34i02.5512} \\
24 & How can the numerical instability of the intersection matrix in skeleton decomposition be mitigated to improve approximation accuracy in self-attention? & \cite{10.1609/aaai.v36i1.19962} \\
25 & How can adversarial perturbations be optimized to concentrate on dominant frequency regions that are consistently influential across different deep neural networks? & \cite{10.1609/aaai.v38i6.28427} \\
26 & How can a high-quality textual relation embedding be learned using global co-occurrence statistics between textual and knowledge base relations as supervision? & \cite{10.18653/v1/p19-1127} \\
27 & How does the scale of transformer language models (e.g., parameter count) influence their ability to process and adapt to atypical animacy, and what does this reveal about their internal representa... & \cite{10.18653/v1/2023.emnlp-main.744} \\
28 & What is the optimal method for identifying the most relevant evidence sentence in an academic abstract that contains the answer to a given question? & \cite{10.1609/aaai.v33i01.33019855} \\
29 & How can the ethical risks of NLP crowdsourcing tasks be systematically assessed using the Belmont Report’s principles to ensure alignment with human-subjects research ethics? & \cite{10.18653/v1/2021.naacl-main.295} \\
30 & How can range-null space decomposition be leveraged to enforce strict data consistency in multi-contrast MRI reconstruction while minimizing information loss? & \cite{10.1609/aaai.v38i2.27869} \\
31 & How do model size, decoding strategies, and prompting with training data affect the novelty of LM-generated text? & \cite{10.18653/v1/2024.emnlp-main.800} \\
32 & How can the integration of re-anchoring with auxiliary strategies like transfer learning and interactive attention further improve the robustness of implicit discourse relation classifiers? & \cite{10.18653/v1/2021.findings-emnlp.110} \\
33 & How can spherical coordinate perturbation and pixelwise depth intervals be combined to refine normal and depth estimates in textureless regions? & \cite{10.1609/aaai.v38i7.28512} \\
34 & How can a single adapter module be trained to adapt a multilingual NMT model to arbitrary new domains and language pairs without requiring domain- or language-specific parameter updates? & \cite{10.18653/v1/2022.findings-emnlp.315} \\
35 & How can a multi-layer funnel pooling strategy in Conformer encoders achieve progressive frame rate reduction while maintaining sufficient temporal resolution for accurate speech recognition? & \cite{10.18653/v1/2024.naacl-long.344} \\
36 & How can an integrated evaluation framework be designed to systematically assess multiple dimensions of metric quality, including correlation, generalization, robustness, and coherence judgment, in ... & \cite{10.18653/v1/2021.acl-long.500} \\
37 & How can an online agent balance adherence to learned behavioral constraints with the need to maximize reward in a dynamic environment? & \cite{10.1609/aaai.v33i01.33013} \\
38 & How can federated learning achieve group fairness through dynamic aggregation weight adjustment based on misalignment between local and global fairness metrics? & \cite{10.1609/aaai.v37i6.25911} \\
39 & Can multilingual transformer models be effectively adapted for cross-lingual acceptability classification tasks, and what are the limitations of this approach for low-resource languages like Italian? & \cite{10.18653/v1/2021.findings-emnlp.250} \\
40 & How can a domain-specific pre-training dataset for Vietnamese hate speech detection be automatically generated to capture the linguistic diversity and contextual complexity of social media content? & \cite{10.18653/v1/2024.findings-acl.355} \\
41 & How can external biomedical knowledge graphs be integrated with AMR representations to improve the understanding of domain-specific entities and events? & \cite{10.18653/v1/2021.acl-long.489} \\
42 & How can a utility function be modified to ensure robustness against (agent × item)-level differential privacy constraints while preserving fairness guarantees? & \cite{10.1609/aaai.v37i5.25721} \\
43 & How can spatial and frequency domain information be effectively fused within a diffusion model to improve low-light image restoration quality? & \cite{10.1609/aaai.v38i5.28273} \\
44 & How can a multi-task training strategy be implemented to jointly optimize hyper-relational KG embedding and contrastive learning objectives without degrading performance? & \cite{10.18653/v1/2024.findings-acl.171} \\
45 & How can manifold learning be integrated with probabilistic modeling to prevent information loss and improve the accuracy of deformation distribution estimation? & \cite{10.1609/aaai.v36i11.21637} \\
46 & How can we learn pose-invariant latent representations for single-view 3D reconstruction that are robust to variations in object orientation? & \cite{10.1609/aaai.v36i1.19920} \\
47 & What is the effectiveness of a RoBERTa-based political stance classifier in identifying biased opinions within generated summaries? & \cite{10.48550/arxiv.2402.00322} \\
48 & How can an adversarial training mechanism be designed to prevent the generator from relying on simple heuristics when producing entailment-aware paraphrases? & \cite{10.1609/aaai.v36i10.21376} \\
49 & What is the impact of incorporating automatically generated affirmative interpretations into the input of pre-trained models for robustness against negation? & \cite{10.18653/v1/2024.acl-short.55} \\
50 & How can a model-agnostic post-processing framework effectively integrate with diverse summarization models without requiring retraining? & \cite{10.18653/v1/2024.findings-acl.59} \\
51 & Can feature-based interpretability methods produce significantly different attributions for functionally equivalent neural text classifiers with distinct random initializations? & \cite{10.18653/v1/2021.findings-acl.327} \\
52 & How can feature importance be leveraged to avoid unnecessary reconstruction of unimportant features during pruning? & \cite{10.1609/aaai.v34i07.6720} \\
53 & How can few-shot learning strategies be integrated with calibration techniques to further reduce miscalibration in Massively Multilingual Language Models (MMLMs) for languages with limited resources? & \cite{10.18653/v1/2022.emnlp-main.290} \\
54 & How can the ReviewCritique dataset be utilized to benchmark the effectiveness of both closed-source and open-source LLMs in scientific peer review tasks? & \cite{10.18653/v1/2024.emnlp-main.292} \\
55 & How can a query-based online search algorithm tolerate up to \$H\$ erroneous binary responses while efficiently narrowing down the optimal price range? & \cite{10.1609/aaai.v36i9.21199} \\
56 & How can Contrastive Decoding be adapted to dynamically adjust its strength based on the confidence of the expert model to avoid degrading non-hallucinated translations? & \cite{10.18653/v1/2024.eacl-long.155} \\
57 & How can channel-wise heterogeneous kernel replacement be designed to adaptively select complementary 1D/2D/3D sub-kernels for each channel in 3D networks? & \cite{10.1609/aaai.v35i4.16433} \\
58 & How can the joint optimization of syntactic structure and visual-semantic alignment be achieved in an end-to-end unsupervised framework? & \cite{10.18653/v1/n19-1180} \\
59 & What graph update mechanism can effectively capture both the relational structure of multi-party dialogues and the temporal evolution of emotional states? & \cite{10.18653/v1/2022.acl-long.24} \\
60 & How can continuous topic-word distributions be sampled in a differentiable manner to enable end-to-end learning of sentiment-aware topics? & \cite{10.18653/v1/2021.eacl-main.199} \\
61 & How can a generative adversarial network be adapted to produce high-quality, class-specific embeddings that enhance few-shot learning without memorizing training examples? & \cite{10.18653/v1/2022.naacl-main.404} \\
62 & How can a shared Attention Residual Gaussian Distribution (ARGD) module enhance the integration of textual information into the posterior path of a variational autoencoder for sign language transla... & \cite{10.1609/aaai.v38i17.29937} \\
63 & How can data augmentation techniques improve the generalization of Gin Rummy hand evaluation models trained on limited or biased datasets? & \cite{10.1609/aaai.v35i17.17843} \\
64 & How can spatio-temporal dependencies in agricultural pricing and volume data be jointly modeled using dual temporal convolutional networks to improve prediction accuracy? & \cite{10.1609/aaai.v34i08.7039} \\
65 & How can a multi-branch mixture density network effectively model the distribution of auction durations by combining game-theoretic predictions with product embeddings? & \cite{10.1609/aaai.v38i9.28854} \\
66 & How can a multi-slot mechanism iteratively specialize variable representations to capture complex contextual dependencies in mathematical text? & \cite{10.18653/v1/2022.findings-acl.76} \\
67 & What are the key structural properties of short clauses and low-occurrence variables that the adaptive branching rules exploit to achieve improved performance over prior methods? & \cite{10.1609/aaai.v35i5.16479} \\
68 & How can a relation classifier be trained to produce confident predictions for individual sentences in an unsupervised setting? & \cite{10.18653/v1/p19-1133} \\
69 & What evaluation metric can effectively measure the quality of predicted explanations by incorporating human judgments of intuitiveness, even when multiple valid explanations exist? & \cite{10.1609/aaai.v36i11.21577} \\
70 & How can zero-shot translation capabilities of multilingual MT models be effectively repurposed for grammatical error correction without task-specific adaptation? & \cite{10.18653/v1/2024.eacl-long.73} \\
71 & How can cell-level layout information be encoded to enable models to recognize semantically coherent units spanning multiple words within a single cell? & \cite{10.18653/v1/2021.acl-long.493} \\
72 & How can the outputs of a pattern-exploitation module be integrated with dynamic context augmentation to improve cross-domain generalization in NED? & \cite{10.18653/v1/2022.findings-emnlp.506} \\
73 & How can dialog systems effectively detect and respond to negative grounding signals (e.g., inconsistencies, errors) to enable collaborative error recovery? & \cite{10.18653/v1/2021.eacl-main.41} \\
74 & How can a time series prediction model dynamically adapt to the distribution of extreme and normal values while maintaining robustness to imbalanced data? & \cite{10.1609/aaai.v37i7.26045} \\
75 & How does subfamily-specific pretraining with custom tokenizers enhance model performance for low-resource languages compared to generic multilingual tokenization strategies? & \cite{10.18653/v1/2023.findings-eacl.93} \\
76 & How can a shared expert mechanism with routing weight normalization be designed to address scale mismatch and improve the effectiveness of sparse upcycling in instruction-tuned code LLMs? & \cite{10.18653/v1/2024.acl-long.699} \\
77 & How can a semantic latent space be identified and utilized for controllable, accumulative, and composable image editing in transformer-based Flow Matching models? & \cite{10.1609/aaai.v38i3.27998} \\
78 & Can language models generalize monotonicity-based NPI licensing to unseen environments without explicit training on NPI occurrences? & \cite{10.18653/v1/2021.findings-acl.439} \\
79 & How can classical optimization techniques be adapted to train quantum classifiers with high accuracy on real-world datasets? & \cite{10.1609/aaai.v35i18.17941} \\
80 & How can an alternating optimization strategy ensure convergence in online pairwise learning without relying on buffer storage or i.i.d. assumptions? & \cite{10.1609/aaai.v38i10.28955} \\
81 & How can NLP and ML research better integrate democratic theories to develop frameworks that ensure equitable participation, accountability, and alignment with democratic values in AI systems? & \cite{10.18653/v1/2024.emnlp-main.184} \\
82 & How does pre-expansion pruning in trie-constrained decoding improve the accuracy and efficiency of parallel sentence retrieval compared to post-expansion pruning? & \cite{10.18653/v1/2020.acl-main.152} \\
83 & How can transferable component prototypes for individual human-annotated attributes be learned and reused to construct compositional representations for novel classes? & \cite{10.1609/aaai.v37i7.26082} \\
84 & How can Chinese characters be effectively transformed into a Latinized stroke sequence representation to leverage subword modeling techniques in NMT? & \cite{10.18653/v1/2022.emnlp-main.434} \\
85 & How can a contrastive self-training framework with adaptive temperature control improve classification performance by balancing confidence and generalization in pseudo-label learning? & \cite{10.18653/v1/2024.eacl-long.39} \\
86 & How can adversarial effectiveness in NMT be evaluated without relying on ground-truth reference translations? & \cite{10.18653/v1/2021.acl-long.153} \\
87 & How can answer spans in paragraphs be leveraged to align answerable and unanswerable question pairs, ensuring both relevance and difficulty? & \cite{10.18653/v1/n19-1415} \\
88 & How can motion conditions be efficiently mapped to tri-plane feature deformations without using 3D parametric models? & \cite{10.1609/aaai.v38i7.28473} \\
89 & How can a TableQA benchmark be constructed to systematically evaluate robustness against diverse, human-annotated adversarial perturbations in table headers, content, and questions? & \cite{10.18653/v1/2023.acl-long.334} \\
90 & How can an alternating optimization algorithm be designed to jointly estimate true labels and train DNN parameters in the presence of instance-dependent label noise? & \cite{10.1609/aaai.v35i11.17221} \\
91 & How can sequential visual and positional features be adaptively fused to improve robustness in UAV navigation under dynamic environmental conditions? & \cite{10.1609/aaai.v38i9.28906} \\
92 & How can latent temporal motion information be effectively predicted and encoded in still images for action recognition? & \cite{10.1609/aaai.v34i03.5653} \\
93 & What architectural design or training strategy enables entity linking models to robustly handle NIL prediction without overfitting to non-NIL examples? & \cite{10.18653/v1/2023.findings-acl.690} \\
94 & How can conversational patterns from the Natural Conversation Framework be systematically integrated into goal-oriented dialog datasets to reflect naturalistic user behavior? & \cite{10.18653/v1/2020.findings-emnlp.358} \\
95 & How does the paper design a pre-training task for multi-hop retrievers that enables iterative document retrieval for sub-questions without requiring human annotations? & \cite{10.18653/v1/2021.findings-acl.62} \\
96 & How can a model determine the optimal position to insert a simile into a given text to maximize contextual coherence? & \cite{10.1609/aaai.v35i16.17691} \\
97 & How can we generate logically coherent answer-explanation pairs in VQA-NLE by modeling reasoning steps as a chain-of-thought process? & \cite{10.1609/aaai.v38i3.28065} \\
98 & How can global property representations be adaptively fused with local sentence features to improve relation prediction? & \cite{10.18653/v1/2022.findings-naacl.128} \\
99 & How can symptom status recognition be improved by formulating it as a natural language inference task that integrates both dialogue context and external medical knowledge? & \cite{10.18653/v1/2023.findings-acl.652} \\
100 & How can the trade-off between attack transferability and stealthiness be dynamically controlled during adversarial perturbation generation in the latent space? & \cite{10.1609/aaai.v38i4.28147} \\
101 & How can human annotation strategies be optimized to effectively evaluate the quality of contrastive explanations in NLP tasks? & \cite{10.18653/v1/2023.emnlp-main.427} \\
102 & How can hard and soft constraints be effectively combined with pre-trained language models to guide high-quality constrained generation without task-specific training? & \cite{10.18653/v1/2020.findings-emnlp.115} \\
103 & How can global label hierarchy be effectively encoded into label embeddings using a pre-trained language model without requiring auxiliary graph encoders or intentional fusion of hierarchical and s... & \cite{10.18653/v1/2022.emnlp-main.268} \\
104 & How can low-performing or data-inefficient clients in federated learning be automatically identified and excluded to improve global model accuracy in autonomous driving simulations? & \cite{10.1609/aaai.v37i13.26984} \\
105 & How can action and information flow relationships between sentences in procedural texts be inferred without explicit named entity recognition or domain-specific rules? & \cite{10.18653/v1/2021.findings-acl.345} \\
106 & How can segmentation uncertainty be quantified and visualized through dynamically adjustable predictive regions that reflect user-specified confidence levels? & \cite{10.1609/aaai.v37i13.26837} \\
107 & How can structured semantic representations for events and arguments be learned from text and visual data in a weakly supervised manner without requiring explicit cross-modal annotations? & \cite{10.18653/v1/2020.acl-main.230} \\
108 & How do different architectural designs and pretraining objectives of pretrained language models affect their ability to capture and represent document-level discourse information across multiple la... & \cite{10.18653/v1/2021.naacl-main.301} \\
109 & Does a text-based hate speech support set outperform a vision-language hate speech support set in few-shot in-context learning for cross-modal hate speech detection? & \cite{10.18653/v1/2024.emnlp-main.445} \\
110 & How can non-autoregressive translation models be trained to progressively learn bilingual knowledge from fine-grained units (words/phrases) to full-sentence structures? & \cite{10.18653/v1/2021.findings-acl.247} \\
111 & How can adversarial test cases be generated by systematically replacing answer-relevant spans in evidence with alternative answers while maintaining contextual coherence? & \cite{10.18653/v1/2024.findings-naacl.85} \\
112 & How can adversarial training be adapted to improve zero-shot cross-lingual transfer by encouraging robustness to embedding misalignments in multilingual representations? & \cite{10.18653/v1/2021.emnlp-main.126} \\
113 & How can the decoder be modified to interpret intermediate encoder representations in encoder-decoder Transformers? & \cite{10.18653/v1/2024.findings-naacl.296} \\
114 & How can the integration of auxiliary tasks during the transition phase improve model stability and prevent catastrophic forgetting when shifting from formal to informal data? & \cite{10.18653/v1/2020.findings-emnlp.282} \\
115 & How can dataset splits be redesigned to mitigate biases from source/time overlap and improve the reliability of evaluation metrics for unreliable news detection? & \cite{10.18653/v1/2021.eacl-main.211} \\
116 & How can patch-level visual patterns from head classes be effectively transferred to tail classes through self-distillation to alleviate their under-representation? & \cite{10.1609/aaai.v38i6.28459} \\
117 & How can a branch-and-bound algorithm be designed to iteratively reduce the relaxation gap of the enhanced SDP relaxation and converge to the exact solution? & \cite{10.1609/aaai.v37i12.26745} \\
118 & How can a value tagger be used to filter noisy or semantically incorrect rewritten utterances in synthesized multi-domain dialogs? & \cite{10.18653/v1/2023.emnlp-main.946} \\
119 & What methods can enable LLMs to engage in meaningful, multi-turn discussions or debates on abstract topics (e.g., philosophy, ethics) while maintaining coherence, avoiding contradictions, and refle... & \cite{10.18653/v1/2023.emnlp-main.146} \\
120 & How can variational inference be adapted to the probabilistic CCA framework to efficiently approximate the posterior distribution of the shared latent variable and view-specific factors in a deep g... & \cite{10.1609/aaai.v35i9.16982} \\
121 & How can a weakly supervised segmentation model be integrated into a detection framework to achieve pixel-level damage localization using only bounding box annotations? & \cite{10.1609/aaai.v34i09.7110} \\
122 & How can a dual decoupling framework effectively separate clean and noisy pseudo boxes to improve training stability and performance in semi-supervised object detection? & \cite{10.1609/aaai.v36i3.20264} \\
123 & How can a funnel-shaped neural network architecture be designed to achieve high compression efficiency while maintaining reconstruction fidelity for spectrum-concentrated data blocks? & \cite{10.1609/aaai.v37i4.25602} \\
124 & How can instrumental variables be generated under unconditional moment restrictions to eliminate confounding effects in graph representation learning? & \cite{10.1609/aaai.v37i6.25925} \\
125 & How can combining embeddings from both shallow and deep layers of a transformer model enhance sentence representation quality? & \cite{10.18653/v1/2021.findings-emnlp.23} \\
126 & How can structured relational knowledge (from hyperlinks) and unstructured factual knowledge (from documents) be dynamically fused during retrieval to improve evidence selection? & \cite{10.1609/aaai.v35i15.17568} \\
127 & How can the capacity of adapter modules be dynamically adjusted to balance performance gains and computational efficiency across tasks with varying data sizes or complexity? & \cite{10.18653/v1/d19-1165} \\
128 & How can a multi-hop selection mechanism be designed to iteratively filter the most relevant context utterances for response matching in multi-turn conversations? & \cite{10.18653/v1/d19-1011} \\
129 & How can symbolic search be combined with neural proof generation to explore diverse and valid proof paths in large search spaces? & \cite{10.18653/v1/2022.emnlp-main.7} \\
130 & How does the hierarchical organization of discourse units, as defined by Rhetorical Structure Theory, influence the predictability of information density fluctuations? & \cite{10.18653/v1/2024.emnlp-main.1047} \\
131 & How can relative position representations improve the modeling of long-range dependencies in source code summarization compared to absolute position encodings? & \cite{10.18653/v1/2020.acl-main.449} \\
132 & How can graph neural networks be designed to efficiently encode high-order dependency relationships in a direction-aware manner? & \cite{10.18653/v1/n19-1237} \\
133 & How can conditional gradients be adapted to enforce global convex constraints in deep neural networks while maintaining computational efficiency and convergence guarantees? & \cite{10.1609/aaai.v33i01.33014772} \\
134 & How can uncertainty-aware contrastive learning be integrated into keypoint detection to improve robustness for texture-less or symmetric objects while maintaining semantic consistency? & \cite{10.1609/aaai.v36i5.20482} \\
135 & How can local correlation analysis of counterfactual examples be used to disentangle syntactic influences from distributional biases in nationality-related name effects? & \cite{10.18653/v1/2024.emnlp-main.34} \\
136 & What treebank selection strategy maximizes parsing performance for low-resource languages by combining training data size and linguistic similarity metrics in an automated, heuristic-driven manner? & \cite{10.18653/v1/2021.findings-acl.431} \\
137 & What automated methods can effectively standardize and annotate complex legal elements (e.g., charges, law articles, penalties) in multi-defendant cases? & \cite{10.18653/v1/2024.findings-acl.351} \\
138 & How can the teaching order of multiple aligners in a cycle-teaching framework be dynamically optimized to maximize overall performance and minimize error propagation? & \cite{10.1609/aaai.v36i4.20348} \\
139 & How can a QA system perform compositional reasoning over complex, logically structured documents to identify answers that depend on conjunctions, disjunctions, or exceptions in the text? & \cite{10.18653/v1/2022.acl-long.253} \\
140 & What is the effectiveness of combining intra-layer self-similarity and inter-layer linear CKA similarity in detecting overfitting of rare and minority group names in neural language models? & \cite{10.18653/v1/2021.emnlp-main.41} \\
141 & What methods can be used to collect and represent high-quality, diverse annotations from multiple annotators while minimizing bias and ensuring reliability? & \cite{10.1609/aaai.v37i6.25840} \\
142 & How can the computational efficiency of inference-based filtering be maintained while ensuring high-quality, coherent story outputs? & \cite{10.18653/v1/2022.findings-emnlp.520} \\
143 & Can the linear optimization problem over the convex polytope \$ C\_\{p\textasciicircum{}\{n+2\}\} \$ be proven \#P-hard, and how does this relate to the verification of semivalues for linear thresh... & \cite{10.1609/aaai.v33i01.33011869} \\
144 & How can multiple distance metrics be combined into a unified loss function to improve cross-lingual alignment performance across diverse language pairs? & \cite{10.18653/v1/2021.findings-acl.276} \\
145 & How can source-side information be utilized to improve the retrieval of relevant examples in kNN-MT? & \cite{10.18653/v1/2023.emnlp-main.503} \\
146 & How can high-quality hard negative samples be generated in the embedding space to improve the discriminative power of contrastive learning for time series? & \cite{10.1609/aaai.v38i12.29299} \\
147 & How can intra-document structural information be utilized to improve the robustness of contrastive learning models against length-induced semantic drift? & \cite{10.18653/v1/2023.emnlp-main.86} \\
148 & How can a collaborative framework integrate panoptic-level selection with region-based refinement to achieve efficient and effective active learning for semantic segmentation? & \cite{10.1609/aaai.v36i2.20107} \\
149 & How can semi-factual data generated using human-identified rationales improve model robustness in few-shot learning without requiring extensive manual intervention? & \cite{10.18653/v1/2022.acl-long.481} \\
150 & How can a scoring mechanism be designed to prioritize functional correctness by emphasizing recall over precision in evaluating code generation quality? & \cite{10.18653/v1/2023.emnlp-main.859} \\
\end{longtable}
